\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-05 manuscript/main.tex
new file:   figures/scatter_plot_with_two_brokerages.pdf 	modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   plotting/same_distribution.ipynb
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.

We can assume that there are $N$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, N\}$ number of houses listed. The houses listed follows a AR(1) model specified by:

@@

\begin{equation}
  p_i = \frac{B_{i, t}}{B_{1, t} + B_{2, t}}. \label{eq:prob}
\end{equation}

The profit of the brokerage in the community is given by $\pi_1(p_1, p_2) = $

@@

@@

To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the other brokerages are also have the same tendency that they typically

This figure is shown in Figure \ref{fig:same_distribution}

@@

>>>>

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market. Each type of brokerage follows a standard percentage charge by $r_j$ and they can not manipulate the percentage charge in each submarket.

We can assume that there are $M$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, M\}$ number of houses listed which depends on the previous listing number and we can formulate it as a AR(1) model specified by:

@@

\begin{equation}
  p_i = \frac{B_{i, t} \times N^e(B_{1, i})}{B_{1, t} \times N^e(B_{1, i}) + B_{2, t}}. \label{eq:prob}
\end{equation}

where $N^e(B_{1, i})$ is a function representing the network effects, and is modeled as $N^e(B_{1, i}) = 1 + \alpha \log(1 + B_{1, i})$ where $\alpha$ is a parameter that quantifies the strength of network effects and the logarithmic form captures diminishing returns to scale as the number of brokerages increases. The revenue for each brokerage type $j$ in community $i$ is proportional to the number of houses they sell, which depends on the number of customers they attract:

\begin{equation}
  R_{i, j, t} = r_j \cdot P_i \cdot N_{i, j, t}
\end{equation}

where $N_{i, j, t}$ is the number of customers selecting type $j$ brokerage in community $i$ at time period $t$, estimated by:

\begin{equation}
  N_{i, j, t} = \lambda_i p_{i, j, t}
\end{equation}

and $\lambda_i$ is the appropriate part of $\lambda$ that arrives in community $i$.

@@

The first proposition is that the charging fee should be higher comparing with type $2$ brokerage.

The second proposition is that the number of stores in high popular regions should be higher in the number of stores and they are more likely to form a network effect.

The third proposition is the introduction of the platform should increase the number of transactions and the number of stores in the market.

The fourth proposition is that the entry of the large brokerage can increase the transaction number and the number of stores in the market.

@@

To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the other brokerages are also have the same tendency that they typically open stores with the same strategy as lianjia, which is consistent with our Theoretical Model's Proposition [xxxxx]. This figure is shown in Figure \ref{fig:same_distribution}.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\textwidth]{../figures/scatter_plot_with_two_brokerages.pdf}
    \caption{Tendency between two types of brokerages}
    \label{fig:same_distribution}
\end{figure}
